Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Borrando comentarios de la revisión al párrafo para cerrar un issue. Closes #25

It is important to note that MUSES does not work as an antivirus itself, but has a sensor which % quizás quitar "has a sensor which" y sólo poner "it"
% Esto ya no sé porque entonces se me repite mucho la palabra "it", serían 2 veces en esta frase y la siguiente que también empieza por "it"...
checks if the device has already an antivirus, and raises a security violation alert if not. It might happen then that the user ignores this advice and the device becomes compromised. As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server. In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will mean a significant change in the patterns. Then, this change in the patterns will be noticed by the server, which will immediately warn the user, and decrease the device trust value.
% [Pedro] aquí pueden preguntar sobre cómo se lleva a cabo esa detección del cambio en los sensores...

>>>>

It is important to note that MUSES does not work as an antivirus itself, but has a sensor which checks if the device has already an antivirus, and raises a security violation alert if not. It might happen then that the user ignores this advice and the device becomes compromised. As it would be explained in the next section, the sensors are constantly sending their monitored values, and therefore patterns are created, stored, and processed on the server. In case the device gets infected with rootkit-type malware \cite{bickford2010rootkits}, a sudden change in the values of the sensors will mean a significant change in the patterns. Then, this change in the patterns will be noticed by the server, which will immediately warn the user, and decrease the device trust value.
